Von Neumann-Morgenstern and Savage Theorems for Causal Decision Making

### 2020-09-16 Artificial_Intelligence_Journal/Draft/AIJ_Draft.tex
ultima version

%Queda la duda de si se necesita especificar un orden previo
\subsection{A random graph approach to causal structure learning}
\label{random_graphs}
For the sake of completeness, we now provide a relaxation of the restriction found in \cite{lattimoreNIPS2016}, \cite{sen2017identifying} and \cite{gonzalez2018playing}: knowing the causal model; in particular, in \cite{gonzalez2018playing} it is required that the graphical structure of the causal model is known, which is a strong assumption. Such assumption is to be relaxed to the case in which the graphical structure of the causal model is unknown, but the variables of the model are known; also, we assume the decision maker has an ordering $\gg$ according to which if $A \gg B$, then $B$ can not cause $A$. Our extension will take on a purely Bayesian approach and make use both of Theorem \ref{causal_savage}, random graphs and the \textit{as if} intuition present in this paper.

@@

Now, we update the $p_{ij}$'s using Bayes Theorem as follows: for each pair of indexes $i,j$ we consider the subgraph containing only $1,i,j,n$ as nodes, either connected or not, and we ask for the probability of such graph producing the output $(X_1 = a^\ast, X_i = x_i, X_j=x_j, X_n=x_n)$, which will be used as the likelihood of data, and as a prior probability we simply use $p_{ij}$, so we have
\begin{equation}{\label{bayesian_updating}}
p_{ij}^{t+1} \propto p(X_1 = a^\ast, X_i = x_i, X_j=x_j, X_n=x_n | \textrm{subgraph formed by nodes 1,i,j,n})p_{ij}^t.
\end{equation}
Then, we update the model generating a new graph according to $p_{ij}$. We do not provide an implementation of Equation \ref{bayesian_updating} as it is not in the scope of this paper.

@@

>>>>

%Queda la duda de si se necesita especificar un orden previo
\subsection{A random graph approach to causal structure learning}
\label{random_graphs}
For the sake of completeness, we now provide a relaxation of the restrictions found in \cite{lattimoreNIPS2016,sen2017identifying,gonzalez2018playing}: knowing the causal model, or some parts of it; in particular, we have mentione that in \cite{gonzalez2018playing} it is required that the graphical structure of the causal model is known, which is a strong assumption. Such assumption is now to be relaxed to the case in which the graphical structure of the causal model is unknown, but the variables of the model are known; also, we assume the decision maker has an ordering $\gg$ according to which if $A \gg B$, then $B$ can not cause $A$. Our extension will take on a purely Bayesian approach and make use both of Theorem \ref{causal_savage}, random graphs and the \textit{as if} intuition present in this paper.

@@

Now, we update the $p_{ij}$'s using Bayes Theorem as follows: for each pair of indexes $i,j$ we consider the subgraph containing only $1,i,j,n$ as nodes, either connected or not, and we ask for the probability of such graph producing the output $(X_1 = a^\ast, X_i = x_i, X_j=x_j, X_n=x_n)$, which will be used as the likelihood of data, and as a prior probability we simply use $p_{ij}$, so we have
\begin{equation}{\label{bayesian_updating}}
p_{ij}^{t+1} \propto p(X_1 = a^\ast, X_i = x_i, X_j=x_j, X_n=x_n | \textrm{current graph})p_{ij}^t.
\end{equation}
Then, we update the model generating a new graph according to $p_{ij}$. We do not provide an implementation of Equation \ref{bayesian_updating} as it is not in the scope of this paper.

@@

\section{Future Work}
In Section \ref{random_graphs} we considered the problem of a decision maker situated in a causal environment who does not fully knows the causal model which controls her environment; previous works have considered different levels of uncertainty over the causal model: knowing conditional distributions, knowing a part of the model, knowing the structure of the model or the variables involved. We leave as future work the case in which the variables of the model are not known and we consider that this scenario could be attacked using tools from Bayesian Nonparametrics \citep{hjort2010bayesian,phadia2013prior} in the form of a prior over causal models, which generates causal graphs of distinct sizes and complexity.
